---
title: "Point Pattern Analysis"
author: "Angel Bogdanov Grigorov"
date: "Created 18 Mar 2023, updated `r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    highlight: tango
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

## Load library

```{r}

library(tidyverse)
library(sf)
library(raster)
# install.packages("spatstat")
library(spatstat)
library(spatstat.data)
#library(maptools)

```

## Load data
```{r}
source("LoadData.R") #  this line runs the LoadData.R script which loads the site and bounding box data into the current environment
source("NNfunction.R") # here we define the NN function getNNAratio()
```


# Run getNNAratio 

for different periods and boxes

```{r NNA-loop}
box_list <- c("Box1", "Box2", "Municipal", "Rectangular")
for (box in box_list) {print(box)}

box <- "Box1"
result <- NULL
mastertable <- NULL

period_list <- c("Pre", "NEO", "CHALCO", "BA","EBA", "IA", "EIA", "LIA", "HELLEN", "RP", "LRP", "LA_","EMA", "HMA", "LMA", 
                 "MA_XIV", "MA_XVII")

# Box loop is not working, use manual box assignment now.
# for (box in box_list){
#   print(box)
#   box <- mget(ls(pattern = paste0(box,"$")))

box <- Box2 #assign different boxes manually
for(period in period_list){
  
    print(period)

  # find period site 
    period_site <- mget(ls(pattern = paste0("^",period,"*")))

      # get the certain period site
  print(period)
  period_site_certain <- period_site[[grep("1_sf$",names(period_site))]]
  
  # calculate NNA on certain period site 
     r_1 <- getNNratio(period_site_certain, box)
  # verification message
     paste0("ratio for ",names(period_site)[[grep("1_sf$",names(period_site))]]," is ", round(r_1, 3))
     
  # get the inclusive-uncertain period site
  period_site_uncertain <- period_site[[grep("2_sf$",names(period_site))]]
  # calculate NNA on certain period site
     r_2 <- getNNratio(period_site_uncertain, box)
     # verification
      paste0("ratio for ",names(period_site)[[grep("2_sf$",names(period_site))]]," is ", round(r_2,3))
  r <- rbind(r_1, r_2)
  colnames(r) <- period
  result <- cbind(result, r)
}

# Save results
# dir.create("../outputs")
write_csv(as.data.frame(result), "../outputs/Box2_NNA.csv")  


#   mastertable <- c(mastertable, result)
# }
```
Note that LBA NNA calculation was erroring out for Box2 so may need to be troubleshot or done manually. 

### Results
#### Prehistoric

```{r result}

# Box 1

Pre_1_Box1 <- getNNratio(Pre_Settl_1_sf, Box1) # Only certain dated settlements

Pre_1_2_Box1 <- getNNratio(Pre_Settl_1_2_sf, Box1) # Including the uncertain dated settlements

```

```{r result}

# Box 2

Pre_1_Box2 <- getNNratio(Pre_Settl_1_sf, Box2) # Only certain dated settlements

Pre_1_2_Box2 <- getNNratio(Pre_Settl_1_2_sf, Box2) # Including the uncertain dated settlement

```

```{r result}

# Rectangular

Pre_1_Rect <- getNNratio(Pre_Settl_1_sf, Rectangular) # Only certain dated settlements

Pre_1_2_Rect <- getNNratio(Pre_Settl_1_2_sf, Rectangular) # Including the uncertain dated settlement

```

```{r result}
# Municipal

Pre_1_Muni <- getNNratio(Pre_Settl_1_sf, Municipal) # Only certain dated settlements

Pre_1_2_Muni <- getNNratio(Pre_Settl_1_2_sf, Municipal) # Including the uncertain dated settlement

```







#### NEO

```{r result}

# Box 1

getNNratio(NEO_Settl_1_sf, Box1) # Only certain dated settlements

getNNratio(NEO_Settl_1_2_sf, Box1) # Including the uncertain dated settlements

```

```{r result}

# Box 2

getNNratio(NEO_Settl_1_sf, Box2) # Only certain dated settlements

getNNratio(NEO_Settl_1_2_sf, Box2) # Including the uncertain dated settlement

```

```{r result}

# Rectangular

getNNratio(NEO_Settl_1_sf, Rectangular) # Only certain dated settlements

getNNratio(NEO_Settl_1_2_sf, Rectangular) # Including the uncertain dated settlement

```

```{r result}
# Municipal

getNNratio(NEO_Settl_1_sf, Municipal) # Only certain dated settlements

getNNratio(NEO_Settl_1_2_sf, Municipal) # Including the uncertain dated settlement

```






#### CHALCO

```{r result}

# Box 1

getNNratio(CHALCO_Settl_1_sf, Box1) # Only certain dated settlements

getNNratio(CHALCO_Settl_1_2_sf, Box1) # Including the uncertain dated settlements

```

```{r result}

# Box 2

getNNratio(CHALCO_Settl_1_sf, Box2) # Only certain dated settlements

getNNratio(CHALCO_Settl_1_2_sf, Box2) # Including the uncertain dated settlement

```

```{r result}

# Rectangular

getNNratio(CHALCO_Settl_1_sf, Rectangular) # Only certain dated settlements

getNNratio(CHALCO_Settl_1_2_sf, Rectangular) # Including the uncertain dated settlement

```

```{r result}
# Municipal

getNNratio(CHALCO_Settl_1_sf, Municipal) # Only certain dated settlements

getNNratio(CHALCO_Settl_1_2_sf, Municipal) # Including the uncertain dated settlement

```


#### BA

```{r result}

# Box 1

getNNratio(BA_Settl_1_sf, Box1) # Only certain dated settlements

getNNratio(BA_Settl_1_2_sf, Box1) # Including the uncertain dated settlements

```

```{r result}

# Box 2

getNNratio(BA_Settl_1_sf, Box2) # Only certain dated settlements

getNNratio(BA_Settl_1_2_sf, Box2) # Including the uncertain dated settlement

```

```{r result}

# Rectangular

getNNratio(BA_Settl_1_sf, Rectangular) # Only certain dated settlements

getNNratio(BA_Settl_1_2_sf, Rectangular) # Including the uncertain dated settlement

```

```{r result}
# Municipal

getNNratio(BA_Settl_1_sf, Municipal) # Only certain dated settlements

getNNratio(BA_Settl_1_2_sf, Municipal) # Including the uncertain dated settlement

```


#### EBA 
```{r result}

# Box 1

getNNratio(EBA_Settl_1_sf, Box1) # Only certain dated settlements

getNNratio(EBA_Settl_1_2_sf, Box1) # Including the uncertain dated settlements

```

```{r result}

# Box 2

getNNratio(EBA_Settl_1_sf, Box2) # Only certain dated settlements

getNNratio(EBA_Settl_1_2_sf, Box2) # Including the uncertain dated settlement

```

```{r result}

# Rectangular

getNNratio(EBA_Settl_1_sf, Rectangular) # Only certain dated settlements

getNNratio(EBA_Settl_1_2_sf, Rectangular) # Including the uncertain dated settlement

```

```{r result}
# Municipal

getNNratio(EBA_Settl_1_sf, Municipal) # Only certain dated settlements

getNNratio(EBA_Settl_1_2_sf, Municipal) # Including the uncertain dated settlement

```


#### LBA
Само 1/2 точки е безсмислено да се прави ПП за тази епоха


#### IA

```{r result}

# Box 1

getNNratio(IA_Settl_1_sf, Box1) # Only certain dated settlements

getNNratio(IA_Settl_1_2_sf, Box1) # Including the uncertain dated settlements

```

```{r result}

# Box 2

getNNratio(IA_Settl_1_sf, Box2) # Only certain dated settlements

getNNratio(IA_Settl_1_2_sf, Box2) # Including the uncertain dated settlement

```

```{r result}

# Rectangular

getNNratio(IA_Settl_1_sf, Rectangular) # Only certain dated settlements

getNNratio(IA_Settl_1_2_sf, Rectangular) # Including the uncertain dated settlement

```

```{r result}
# Municipal

getNNratio(IA_Settl_1_sf, Municipal) # Only certain dated settlements

getNNratio(IA_Settl_1_2_sf, Municipal) # Including the uncertain dated settlement

```


#### ΙΕΑ 
```{r result}

# Box 1

getNNratio(EIA_Settl_1_sf, Box1) # Only certain dated settlements

getNNratio(EIA_Settl_1_2_sf, Box1) # Including the uncertain dated settlements

```

```{r result}

# Box 2

getNNratio(EIA_Settl_1_sf, Box2) # Only certain dated settlements

getNNratio(EIA_Settl_1_2_sf, Box2) # Including the uncertain dated settlement

```

```{r result}

# Rectangular

getNNratio(EIA_Settl_1_sf, Rectangular) # Only certain dated settlements

getNNratio(EIA_Settl_1_2_sf, Rectangular) # Including the uncertain dated settlement

```

```{r result}
# Municipal

getNNratio(EIA_Settl_1_sf, Municipal) # Only certain dated settlements

getNNratio(EIA_Settl_1_2_sf, Municipal) # Including the uncertain dated settlement

```


#### LIA

```{r result}

# Box 1

getNNratio(LIA_Settl_1_sf, Box1) # Only certain dated settlements

getNNratio(LIA_Settl_1_2_sf, Box1) # Including the uncertain dated settlements

```

```{r result}

# Box 2

getNNratio(LIA_Settl_1_sf, Box2) # Only certain dated settlements

getNNratio(LIA_Settl_1_2_sf, Box2) # Including the uncertain dated settlement

```

```{r result}

# Rectangular

getNNratio(LIA_Settl_1_sf, Rectangular) # Only certain dated settlements

getNNratio(LIA_Settl_1_2_sf, Rectangular) # Including the uncertain dated settlement

```

```{r result}
# Municipal

getNNratio(LIA_Settl_1_sf, Municipal) # Only certain dated settlements

getNNratio(LIA_Settl_1_2_sf, Municipal) # Including the uncertain dated settlement

```


#### HELLEN

```{r result}
# Box 1

getNNratio(HELLEN_Settl_1_sf, Box1) # Only certain dated settlements

getNNratio(HELLEN_Settl_1_2_sf, Box1) # Including the uncertain dated settlements

```

```{r result}

# Box 2

getNNratio(HELLEN_Settl_1_sf, Box2) # Only certain dated settlements

getNNratio(HELLEN_Settl_1_2_sf, Box2) # Including the uncertain dated settlement

```

```{r result}

# Rectangular

getNNratio(HELLEN_Settl_1_sf, Rectangular) # Only certain dated settlements

getNNratio(HELLEN_Settl_1_2_sf, Rectangular) # Including the uncertain dated settlement

```

```{r result}
# Municipal

getNNratio(HELLEN_Settl_1_sf, Municipal) # Only certain dated settlements

getNNratio(HELLEN_Settl_1_2_sf, Municipal) # Including the uncertain dated settlement

```


#### RP

```{r result}
# Box 1

getNNratio(RP_Settl_1_sf, Box1) # Only certain dated settlements

getNNratio(RP_Settl_1_2_sf, Box1) # Including the uncertain dated settlements

```

```{r result}

# Box 2

getNNratio(RP_Settl_1_sf, Box2) # Only certain dated settlements

getNNratio(RP_Settl_1_2_sf, Box2) # Including the uncertain dated settlement

```

```{r result}

# Rectangular

getNNratio(RP_Settl_1_sf, Rectangular) # Only certain dated settlements

getNNratio(RP_Settl_1_2_sf, Rectangular) # Including the uncertain dated settlement

```

```{r result}
# Municipal

getNNratio(RP_Settl_1_sf, Municipal) # Only certain dated settlements

getNNratio(RP_Settl_1_2_sf, Municipal) # Including the uncertain dated settlement

```


#### LRP

```{r result}
# Box 1

getNNratio(LRP_Settl_1_sf, Box1) # Only certain dated settlements

getNNratio(LRP_Settl_1_2_sf, Box1) # Including the uncertain dated settlements

```

```{r result}

# Box 2

getNNratio(LRP_Settl_1_sf, Box2) # Only certain dated settlements

getNNratio(LRP_Settl_1_2_sf, Box2) # Including the uncertain dated settlement

```

```{r result}

# Rectangular

getNNratio(LRP_Settl_1_sf, Rectangular) # Only certain dated settlements

getNNratio(LRP_Settl_1_2_sf, Rectangular) # Including the uncertain dated settlement

```

```{r result}
# Municipal

getNNratio(LRP_Settl_1_sf, Municipal) # Only certain dated settlements

getNNratio(LRP_Settl_1_2_sf, Municipal) # Including the uncertain dated settlement

```


#### LA

```{r result}
# Box 1

getNNratio(LA_Settl_1_sf, Box1) # Only certain dated settlements

getNNratio(LA_Settl_1_2_sf, Box1) # Including the uncertain dated settlements

```

```{r result}

# Box 2

getNNratio(LA_Settl_1_sf, Box2) # Only certain dated settlements

getNNratio(LA_Settl_1_2_sf, Box2) # Including the uncertain dated settlement

```

```{r result}

# Rectangular

getNNratio(LA_Settl_1_sf, Rectangular) # Only certain dated settlements

getNNratio(LA_Settl_1_2_sf, Rectangular) # Including the uncertain dated settlement

```

```{r result}
# Municipal

getNNratio(LA_Settl_1_sf, Municipal) # Only certain dated settlements

getNNratio(LA_Settl_1_2_sf, Municipal) # Including the uncertain dated settlement

```


#### EMA

```{r result}
# Box 1

getNNratio(EMA_Settl_1_sf, Box1) # Only certain dated settlements

getNNratio(EMA_Settl_1_2_sf, Box1) # Including the uncertain dated settlements

```

```{r result}

# Box 2

getNNratio(EMA_Settl_1_sf, Box2) # Only certain dated settlements

getNNratio(EMA_Settl_1_2_sf, Box2) # Including the uncertain dated settlement

```

```{r result}

# Rectangular

getNNratio(EMA_Settl_1_sf, Rectangular) # Only certain dated settlements

getNNratio(EMA_Settl_1_2_sf, Rectangular) # Including the uncertain dated settlement

```

```{r result}
# Municipal

getNNratio(EMA_Settl_1_sf, Municipal) # Only certain dated settlements

getNNratio(EMA_Settl_1_2_sf, Municipal) # Including the uncertain dated settlement

```


#### HMA

```{r result}
# Box 1

getNNratio(HMA_Settl_1_sf, Box1) # Only certain dated settlements

getNNratio(HMA_Settl_1_2_sf, Box1) # Including the uncertain dated settlements

```

```{r result}

# Box 2

getNNratio(HMA_Settl_1_sf, Box2) # Only certain dated settlements

getNNratio(HMA_Settl_1_2_sf, Box2) # Including the uncertain dated settlement

```

```{r result}

# Rectangular

getNNratio(HMA_Settl_1_sf, Rectangular) # Only certain dated settlements

getNNratio(HMA_Settl_1_2_sf, Rectangular) # Including the uncertain dated settlement

```

```{r result}
# Municipal

getNNratio(HMA_Settl_1_sf, Municipal) # Only certain dated settlements

getNNratio(HMA_Settl_1_2_sf, Municipal) # Including the uncertain dated settlement

```


#### LMA

```{r result}
# Box 1

getNNratio(LMA_Settl_1_sf, Box1) # Only certain dated settlements

getNNratio(LMA_Settl_1_2_sf, Box1) # Including the uncertain dated settlements

```

```{r result}

# Box 2

getNNratio(LMA_Settl_1_sf, Box2) # Only certain dated settlements

getNNratio(LMA_Settl_1_2_sf, Box2) # Including the uncertain dated settlement

```

```{r result}

# Rectangular

getNNratio(LMA_Settl_1_sf, Rectangular) # Only certain dated settlements

getNNratio(LMA_Settl_1_2_sf, Rectangular) # Including the uncertain dated settlement

```

```{r result}
# Municipal

getNNratio(LMA_Settl_1_sf, Municipal) # Only certain dated settlements

getNNratio(LMA_Settl_1_2_sf, Municipal) # Including the uncertain dated settlement

```


#### MA_XIV

```{r result}
# Box 1

getNNratio(MA_XIV_Settl_1_sf, Box1) # Only certain dated settlements

getNNratio(MA_XIV_Settl_1_2_sf, Box1) # Including the uncertain dated settlements

```

```{r result}

# Box 2

getNNratio(MA_XIV_Settl_1_sf, Box2) # Only certain dated settlements

getNNratio(MA_XIV_Settl_1_2_sf, Box2) # Including the uncertain dated settlement

```

```{r result}

# Rectangular

getNNratio(MA_XIV_Settl_1_sf, Rectangular) # Only certain dated settlements

getNNratio(MA_XIV_Settl_1_2_sf, Rectangular) # Including the uncertain dated settlement

```

```{r result}
# Municipal

getNNratio(MA_XIV_Settl_1_sf, Municipal) # Only certain dated settlements

getNNratio(MA_XIV_Settl_1_2_sf, Municipal) # Including the uncertain dated settlement

```


#### MA_XVII

```{r result}
# Box 1

getNNratio(MA_XVII_Settl_1_sf, Box1) # Only certain dated settlements

getNNratio(MA_XVII_Settl_1_2_sf, Box1) # Including the uncertain dated settlements

```

```{r result}

# Box 2

getNNratio(MA_XVII_Settl_1_sf, Box2) # Only certain dated settlements

getNNratio(MA_XVII_Settl_1_2_sf, Box2) # Including the uncertain dated settlement

```

```{r result}

# Rectangular

getNNratio(MA_XVII_Settl_1_sf, Rectangular) # Only certain dated settlements

getNNratio(MA_XVII_Settl_1_2_sf, Rectangular) # Including the uncertain dated settlement

```

```{r result}
# Municipal

getNNratio(MA_XVII_Settl_1_sf, Municipal) # Only certain dated settlements

getNNratio(MA_XVII_Settl_1_2_sf, Municipal) # Including the uncertain dated settlement

```

Steps: 

1) generate owin for Box 1 or 2 simple features
2) intersect points with sf of Box 1 and 2 and convert the result to ppp object
3) run the nndist and r calculations

Prehist






